---
title: "Cats data analysis to practice WORCS"
output: github_document
date: '`r format(Sys.time(), "%d %B, %Y")`'
bibliography: references.bib
knit: worcs::cite_all
---

```{r setup, include=FALSE}
library("worcs")
load_data()
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# Some visuals and analyses to be reproduced 

# Which breed has the lowest mean weight?
library(ggplot2)
ggplot(CatsData, aes(x = weight, y = breed)) +
  geom_boxplot()

# Which cat has the highest observed weight?
CatsData[which.max(CatsData$weight),]
```
The Persian breed has the lowest mean weight. The heaviest cat (22.9 lbs measured in 2018) is a male American Shorthair cat of 3 years old in clinic 17, owned by client 20, living in a suburban area. 

This manuscript uses the Workflow for Open Reproducible Code in Science [@vanlissaWORCSWorkflowOpen2020] to ensure reproducibility and transparency. All code <!--and data--> are available at <git@github.com:Rasila/tryWORCS.git>.

<!--The function below inserts a notification if the manuscript is knit using synthetic data. Make sure to insert it after load_data().-->
`r notify_synthetic()`


